## Setup

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```
```{r}
library(targets)
library(dplyr)
library(EpiSewer)
library(ggplot2)
source("code/pipeline/utils_pipeline.R")
source("code/pipeline/utils_real_time.R")
source("data/assumptions/epi_params_EpiSewer-study.R")
source("code/local_config.R")
```

Create pipeline folders if they do not exist
```{r}
setup_pipeline("_overview_22-23")
setup_pipeline("_overview_23-24")
setup_pipeline("_overview_24-25")
```

## Run pipelines
Explanation for pipelines: If a pipeline is run for the first time, it will create all required objects and and submit all missing jobs for model fitting (if submit = TRUE). After the pipeline is finished and all models have been fitted, you will have to run it a second time to load the results, but this will not re-fit the models (=> much faster).

```{r, include = FALSE}
run_pipeline(targets_proj_name = "_overview_22-23", submit = TRUE)
if(length(tar_read(jobs_EpiSewer_invalid))>0) {
  warning("There are invalid jobs.")
}
```

```{r, include = FALSE}
run_pipeline(targets_proj_name = "_overview_23-24", submit = TRUE)
if(length(tar_read(jobs_EpiSewer_invalid))>0) {
  warning("There are invalid jobs.")
}
```

```{r, include = FALSE}
run_pipeline(targets_proj_name = "_overview_24-25", submit = TRUE)
if(length(tar_read(jobs_EpiSewer_invalid))>0) {
  warning("There are invalid jobs.")
}
```

Check results
```{r}
rbindlist(lapply(c("_overview_22-23", "_overview_23-24", "_overview_24-25"), function(pipeline) {
  suppressMessages(setup_pipeline(pipeline))
  return(tar_read(job_EpiSewer_submission) |>
    mutate(total = 1, .before = exists) |>
    summarise(across(total:submitted, \(x) sum(x, na.rm = TRUE))) |> 
    mutate(pipeline = pipeline, .before = total)
    )
}))
```

## Load results

```{r}
all_pipelines <- c("_overview_22-23", "_overview_23-24", "_overview_24-25")
job_EpiSewer_result <- load_EpiSewer_results(all_pipelines)
data_PCR_agg_select <- get_data_PCR_agg_select(all_pipelines)
data_flow_select <- get_data_flow_select(all_pipelines)
```

Build index
```{r}
results_index <- bind_rows(lapply(job_EpiSewer_result, function(x) {
  if (length(x) == 0) { data.frame(wwtp = NA, target = NA, estimation_date = NA)
  } else {
    return(data.frame(
      wwtp = x$job$selection$wwtp,
      target = x$job$selection$target,
      estimation_date = lubridate::as_date(x$job$selection$date_select[[1]]["to"]),
      season = case_when(
        lubridate::as_date(x$job$selection$date_select[[1]]["to"])<"2023-08-01" ~ "2022/23",
        lubridate::as_date(x$job$selection$date_select[[1]]["to"])<"2024-08-01" ~ "2023/24",
        lubridate::as_date(x$job$selection$date_select[[1]]["to"])<"2025-08-01" ~ "2024/25",
        TRUE ~ "Unknown"
      )
  ))}
  }))
rownames(results_index) <- NULL
results_index$i <- 1:nrow(results_index)

get_result_label <- function(x) {
  paste(
    x$summary$R[type == "estimate", max(date)],
    x$job$selection$wwtp,
    x$job$selection$target
    )
}
```

### Determine wave dates
In the following, we define the start and end of the respective seasonal waves of SARS-CoV-2, IAV, and RSV based on the estimated time series of infections.
```{r}
count_detect_runs <- function(detect){
    sapply(1:length(detect), function(i) {
      if (all(detect[i:length(detect)])) {
        return(length(detect) - i + 1)
      } else {
        return(which.min(detect[i:length(detect)])[1] - 1)
      }
    })
  }
```

Start: First week in second half of year with a 10% weekly growth rate and no consecutive non-detects before the peak
End: First week three months after peak with less than 10% weekly decline
```{r}
results_index$start_date <- as.Date(apply(results_index, 1, function(result_select) {
  if (is.na(result_select["wwtp"])) return(NA)
  peak <- job_EpiSewer_result[[as.numeric(result_select["i"])]]$summary$expected_infections[type == "estimate",][median == max(median, na.rm = T)]
  stopifnot(nrow(peak)>0)
  lcc <- job_EpiSewer_result[[as.numeric(result_select["i"])]]$job$metainfo$load_curve_crude
  lcc[!is.na(detect), nondetect_next_n := count_detect_runs(!detect)]
  if (nrow(lcc[date <= peak$date & nondetect_next_n >= 2,])>0) {
      last_double_nondetect <- lcc[date <= peak$date & nondetect_next_n >= 2, max(date)]
      min_date_detects <- lcc[date >= last_double_nondetect & detect, min(date)]
  } else {
      min_date_detects <- as.Date("1999-01-01")
  }
job_EpiSewer_result[[as.numeric(result_select["i"])]]$summary$infections |> mutate(isoyear = lubridate::isoyear(date), isoweek = lubridate::isoweek(date)) |> group_by(isoyear, isoweek) |> summarize(date = min(date), weekly_incidence = 7*mean(mean), .groups = "drop") |> 
    filter(date >= paste0(lubridate::year(min(date, na.rm = T)), "-09-01"), date >= min_date_detects) |> 
    filter(weekly_incidence/lag(weekly_incidence) > 1.1) |> slice_head() |> pull(date) |> as.character()
}))

results_index$end_date <- as.Date(apply(results_index, 1, function(result_select) {
  if (is.na(result_select["wwtp"])) return(NA)
  peak <- job_EpiSewer_result[[as.numeric(result_select["i"])]]$summary$expected_infections[type == "estimate",][median == max(median),]
  wave_ts <- job_EpiSewer_result[[as.numeric(result_select["i"])]]$summary$expected_infections |> 
    mutate(isoyear = lubridate::isoyear(date), isoweek = lubridate::isoweek(date)) |> 
    group_by(isoyear, isoweek) |> 
    summarize(date = min(date), incidence_week_avg = mean(mean), .groups = "drop") |> 
    mutate(weekly_growth = incidence_week_avg/lag(incidence_week_avg)) 
  
  bind_rows(
    wave_ts |> filter(date > peak$date + 3*4*7, weekly_growth > 0.9),
    wave_ts |> slice_tail() # fallback, latest modeled date
  ) |>   
    slice_head() |> 
    pull(date) |> 
    as.character()
  }))

results_index <- results_index |> mutate(
  start_date_data = start_date - 4*7,
  end_date_model = end_date + 8*7
)
```

Correct SARS-CoV-2 end dates of wave for season 2022/23 (account for additional spring wave)
```{r}
setDT(results_index)
results_index[season == "2022/23" & wwtp == "ARA Werdhoelzli" & target == "SARS-N2", end_date_model := as.Date("2023-06-01")]
results_index[season == "2022/23" & wwtp == "ARA Werdhoelzli" & target == "SARS-N2", end_date := end_date_model - 8*7]

results_index[season == "2022/23" & wwtp == "CDA Lugano" & target == "SARS-N2", end_date_model := as.Date("2023-06-01")]
results_index[season == "2022/23" & wwtp == "CDA Lugano" & target == "SARS-N2", end_date := end_date_model - 8*7]

results_index[season == "2022/23" & wwtp == "ARA Chur" & target == "SARS-N2", end_date_model := as.Date("2023-06-01")]
results_index[season == "2022/23" & wwtp == "ARA Chur" & target == "SARS-N2", end_date := end_date_model - 8*7]

results_index[season == "2022/23" & wwtp %in% c("ARA Werdhoelzli", "CDA Lugano", "ARA Chur") & target == "SARS-N2",]

results_index <- as_tibble(results_index)
```

```{r}
wwtps_select <- c("ARA Werdhoelzli", "CDA Lugano", "ARA Chur")

results_index |> 
  filter(wwtp %in% wwtps_select) |> 
  mutate(
    wwtp = factor(wwtp, levels = wwtps_select, ordered = T),
    target = factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), ordered = T)
    ) |> 
  arrange(season, target, wwtp) |>
  relocate(start_date_data, .before = start_date) |> 
  relocate(end_date_model, .after = start_date)
```

Save wave dates
```{r}
results_index |> select(wwtp, target, season, start_date, start_date_data, end_date, end_date_model) |> 
  readr::write_csv(here::here("data", "assumptions", "wave_dates.csv"))
```

### Detected outliers
```{r}
detected_outliers <- apply(results_index, 1, function(x) {
  res <- job_EpiSewer_result[[as.numeric(x["i"])]]$summary$outliers
  if (is.null(res)) return(NULL)
  outlier_df <- res[epsilon > 1, c("date", "epsilon")]
  outlier_df[ , wwtp := x["wwtp"][1]]
  outlier_df[ , target := x["target"][1]]
  outlier_df[ , outlier_detected := TRUE]
  data.table::setcolorder(outlier_df, c("wwtp", "target", "date", "outlier_detected", "epsilon"))
  return(outlier_df)
})
```

```{r}
for (season_i in c("2022/23","2023/24","2024/25")) {
  detected_outliers_scores <- lapply(detected_outliers[results_index |> filter(season == season_i) |> pull(i)], function(x) {
  x |> mutate(q = sapply(epsilon, function(e) extraDistr::pgev(q = e, mu = 0, sigma = 2e-8, xi = 4)))
})
print(bind_rows(detected_outliers_scores[sapply(detected_outliers_scores, function(x) nrow(x)>0)]))
}
```
### Analysis of concentrations

Peak concentration
```{r}
results_index |> mutate(peak_concentration = apply(results_index, 1, function(x) {
  outliers <- detected_outliers[[as.numeric(x["i"])]]
  data_PCR_agg_select[[as.numeric(x["i"])]][!(date %in% outliers$date), max(gc_per_mlww)]
})) |> filter(wwtp %in% wwtps_select)

results_index |> mutate(peak_concentration = apply(results_index, 1, function(x) {
  outliers <- detected_outliers[[as.numeric(x["i"])]]
  data_PCR_agg_select[[as.numeric(x["i"])]][!(date %in% outliers$date), max(gc_per_mlww)]
})) |> group_by(target, season) |> summarize(min_peak_concentration = min(peak_concentration), max_peak_concentration = max(peak_concentration))
```

Median concentration
```{r}
results_index |> mutate(peak_concentration = apply(results_index, 1, function(x) {
  outliers <- detected_outliers[[as.numeric(x["i"])]]
  data_PCR_agg_select[[as.numeric(x["i"])]][!(date %in% outliers$date), median(gc_per_mlww)]
})) |> filter(wwtp %in% wwtps_select)
```

Percentage of non-detects
```{r}
results_index |> mutate(share_nondetect = apply(results_index, 1, function(x) {
  cutoff <- case_when(x["season"]=="2022/23" ~ "2023-01-01", x["season"]=="2023/24" ~ "2024-01-01", x["season"]=="2024/25" ~ "2025-01-01")
  data_PCR_agg_select[[as.numeric(x["i"])]][date < cutoff, sum(gc_per_mlww == 0)/.N]
})) |> group_by(target, season) |> 
  summarize(min_share_nondetect = min(share_nondetect), max_share_nondetect = max(share_nondetect)) |> 
  mutate(across(c(min_share_nondetect, max_share_nondetect), scales::percent))
```

### Model fit

Coverage of posterior predictive measurement distribution
```{r}
results_index |> mutate(coverage_q95 = apply(results_index, 1, function(x) {
  if (is.null(job_EpiSewer_result[[as.numeric(x["i"])]]$summary$concentration)) return(NA)
  preds <- merge(
    data_PCR_agg_select[[as.numeric(x["i"])]][, c("date", "gc_per_mlww")],
    job_EpiSewer_result[[as.numeric(x["i"])]]$summary$concentration,
    by = "date"
    )
  return(preds[type == "estimate" & gc_per_mlww > 0, sum(gc_per_mlww >= lower_0.95 & gc_per_mlww <= upper_0.95)/sum(!is.na(gc_per_mlww))])
})) |> group_by(season, target) |>
   filter(coverage_q95 > 0) |> 
   summarize(mean_coverage_q95 = mean(coverage_q95), min_coverage_q95 = min(coverage_q95), max_coverage_q95 = max(coverage_q95))

results_index |> mutate(coverage_q5 = apply(results_index, 1, function(x) {
  if (is.null(job_EpiSewer_result[[as.numeric(x["i"])]]$summary$concentration)) return(NA)
  preds <- merge(
    data_PCR_agg_select[[as.numeric(x["i"])]][, c("date", "gc_per_mlww")],
    job_EpiSewer_result[[as.numeric(x["i"])]]$summary$concentration,
    by = "date"
    )
  return(preds[type == "estimate" & gc_per_mlww > 0, sum(gc_per_mlww >= lower_0.5 & gc_per_mlww <= upper_0.5)/sum(!is.na(gc_per_mlww))])
})) |> group_by(season, target) |> 
  filter(coverage_q5 > 0) |> 
  summarize(mean_coverage_q5 = mean(coverage_q5), min_coverage_q5 = min(coverage_q5), max_coverage_q5 = max(coverage_q5))
```

### Estimated peaks
```{r}
results_index |> mutate(
  peak_median = apply(results_index, 1, function(x) {
  res <- job_EpiSewer_result[[as.numeric(x["i"])]]$summary$R
  if (is.null(res)) return(NA)
  if (x[["season"]] == "2022/23") {
    return(as.character(res[date >= "2022-10-15" & median <= 1, min(date)]))
  } else if (x[["season"]] == "2023/24") {
    return(as.character(res[date >= "2023-10-15" & median <= 1, min(date)]))
  } else if (x[["season"]] == "2024/25") {
    return(as.character(res[date >= "2024-10-15" & median <= 1, min(date)]))
  } else {
    return(NA)
  }
})) |> filter(!(wwtp %in% c("STEP Vidy", "ARA Basel/Prorheno", "ARA Buholz") & target == "IAV-M")) |>
  group_by(target, season) |> 
  summarize(min_peak = min(peak_median, na.rm = T), max_peak = max(peak_median, na.rm = T))
```

### Maximum Rt
```{r}
results_index |> mutate(
  R_max_median = apply(results_index, 1, function(x) {
  res <- job_EpiSewer_result[[as.numeric(x["i"])]]$summary$R
  if (is.null(res)) return(NA)
  if (x[["season"]] == "2022/23") {
    return(as.character(res[date >= "2022-09-01", max(median, na.rm = T)]))
  } else if (x[["season"]] == "2023/24") {
    return(as.character(res[date >= "2023-09-01", max(median, na.rm = T)]))
  } else if (x[["season"]] == "2024/25") {
    return(as.character(res[date >= "2024-09-01", max(median, na.rm = T)]))
  }
})) |> filter(wwtp %in% wwtps_select) |> 
  group_by(target, season) |> 
  summarize(min_Rmax = as.numeric(min(R_max_median, na.rm = T)), max_Rmax = as.numeric(max(R_max_median, na.rm = T))) |> 
  mutate(across(c(min_Rmax, max_Rmax), round, 2))
```

### Overview figure
```{r}
palette_targets <- c("#BC3C29FF","#0072B5FF","#E18727FF")
```

```{r}
fontfam <- "sans"
```

Plotting function
```{r fig.width = 10, fig.height = 12}
get_wwtp_panels <- function(season_select, wwtps_select, use_growth_rate = FALSE, show_flow = TRUE) {
  
  if (season_select == "2022/23") {
    date_lim <- as.Date(c("2022-11-15", "2023-04-15"))
    target_R_lim <- list(
    `SARS-N2` = c(0.65, 1.3),
    `IAV-M` = c(0.6, 1.8),
    `RSV-N` = c(0.5, 1.7)
  )
    target_r_lim <- list(
    `SARS-N2` = c(-0.12, 0.12),
    `IAV-M` = c(-0.2, 0.2),
    `RSV-N` = c(-0.12, 0.12)
  )
  target_R_breaks <- list(
    `SARS-N2` = c(0.8, 1, 1.2),
    `IAV-M` = c(0.7, 1, 1.4),
    `RSV-N` = c(1, 1.5)
  )
  } else if (season_select == "2023/24") {
    date_lim <- as.Date(c("2023-08-30", "2024-04-15"))
    target_R_lim <- list(
    `SARS-N2` = c(0.7, 1.3),
    `IAV-M` = c(0.6, 1.5),
    `RSV-N` = c(0.6, 1.9)
  )
    target_r_lim <- list(
    `SARS-N2` = c(-0.12, 0.12),
    `IAV-M` = c(-0.15, 0.15),
    `RSV-N` = c(-0.12, 0.12)
  )
  target_R_breaks <- list(
    `SARS-N2` = c(0.8, 1, 1.2),
    `IAV-M` = c(0.7, 1, 1.4),
    `RSV-N` = c(1, 1.5)
  )
  } else if (season_select == "2024/25") {
    date_lim <- as.Date(c("2024-08-30", "2025-04-15"))
    target_R_lim <- list(
    `SARS-N2` = c(0.7, 1.3),
    `IAV-M` = c(0.6, 1.6),
    `RSV-N` = c(0.6, 2.0)
  )
    target_r_lim <- list(
    `SARS-N2` = c(-0.12, 0.12),
    `IAV-M` = c(-0.17, 0.17),
    `RSV-N` = c(-0.12, 0.12)
  )
  target_R_breaks <- list(
    `SARS-N2` = c(0.8, 1, 1.2),
    `IAV-M` = c(0.7, 1, 1.4),
    `RSV-N` = c(1, 1.8)
  )
  }
    
  target_labels <- list(
    `SARS-N2` = "SARS-CoV-2",
    `IAV-M` = "IAV",
    `RSV-N` = "RSV"
  )
  
  style_x <- function(g) {
      g + scale_x_date(date_breaks = "2 months", date_labels = "%b '%y", expand = c(0,0))
  }
    
  remove_y <- function(g) {
    g + theme(
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
  }
  
  return(suppressMessages(
  lapply(1:length(wwtps_select), function(wwtp_select_i) {
  wwtp_select <- wwtps_select[wwtp_select_i]
  baseline_select_list <- lapply(c("SARS-N2", "IAV-M", "RSV-N"), function(target_select) {
    results_index |> filter(wwtp == wwtp_select, target == target_select, season == season_select)
  })
  
  flow_data <- data_flow_select[[baseline_select_list[[1]]$i]] |> 
    filter(imputed==FALSE, date >= date_lim[1], date <= date_lim[2]) |> 
    mutate(wwtp = factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T))
  max_flow <- max(flow_data$flow, na.rm = T)
  
  flow_plot <- flow_data |> 
    ggplot(aes(x=date, y = flow)) + 
    geom_point(shape = 4, size = 0.8) +
    geom_line(linetype = "dashed", linewidth = 0.2, color = "grey") +
    geom_smooth(span = 4*7 / length(unique(flow_data$date)), se = FALSE, linetype = "solid", color = "#4d4d4d") +
    scale_x_date(date_breaks = "2 months", date_labels = "%b '%y", expand = expansion(add=c(0,0))) +
    scale_y_continuous(labels = function(x) paste0(round(x/max_flow*100), "%"), breaks = max_flow * seq(0,2,0.5)) +
    xlab("Date") +
    ylab(expression(flow[t]/flow[max])) +
    theme_bw() +
    theme(
      axis.title.x = element_blank(),
      axis.ticks = element_blank(),
      panel.border = element_blank(),
      text = element_text(family = fontfam),
      axis.text.y = element_text(angle = 90, hjust = 0.5)
      ) +
    coord_cartesian(xlim = date_lim, ylim = c(0, max_flow*1.05))

  if (wwtp_select_i > 1) {
      flow_plot <- remove_y(flow_plot)
    }
  if (wwtp_select_i == length(wwtps_select)) {
      flow_strip <- cowplot::plot_grid(
        NULL,
        cowplot::get_plot_component(
          ggplot(data.frame(label="Flow volume")) + 
        facet_grid(label ~ ., scales = "free_y") + 
        theme(
          strip.text.y = element_text(angle = -90),
          strip.background = element_rect(fill = "#f2f2f2", color = "black")
          ),
          pattern = "strip-r-1"),
        NULL, ncol = 1, rel_heights = c(0.025, 0.95, 0.12))
      
     flow_part <- cowplot::plot_grid(
        flow_plot, flow_strip, nrow = 1, rel_widths = c(0.9, 0.1)
        ) 
  } else {
    flow_part <- flow_plot
  }

  main_plots <- lapply(1:3, function(j) {
    i_select <- baseline_select_list[[j]]$i
    target_select <- baseline_select_list[[j]]$target
    color_select <- palette_targets[j]
    
    max_concentration <- data_PCR_agg_select[[i_select]][is_outlier == FALSE, max(gc_per_mlww)]
    
    concentration_plot <- plot_concentration(
      setNames(list(job_EpiSewer_result[[i_select]]), target_labels[[target_select]]),
      measurements = data_PCR_agg_select[[i_select]],
      concentration_col = "gc_per_mlww", intervals = c(0.5, 0.95),
      forecast = FALSE, median = T, obs_size = 1, obs_shape = 16
      ) +
      theme(
        strip.background = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        text = element_text(family = fontfam),
        axis.text.y = element_text(angle = 90, hjust = 0.5)
        ) +
      scale_y_continuous(
        labels = function(x) paste0(round(x/max_concentration*100), "%"),
        breaks = max_concentration * seq(0,2,0.5)
        ) +
      coord_cartesian(xlim = date_lim, ylim = c(0, max_concentration*1.2)) + 
      ylab(expression(c[t]/c[max])) +
      scale_color_manual(values = color_select) +
      scale_fill_manual(values = color_select)
    
    if (use_growth_rate) {
        transmission_plot <- plot_growth_rate(
        setNames(list(job_EpiSewer_result[[i_select]]), target_select),
        forecast = FALSE, median = T, intervals = c(0.5, 0.95), seeding = TRUE
        ) +
        coord_cartesian(xlim = date_lim, ylim = target_r_lim[[target_select]]) +
        ylab("Growth rate") +
        scale_y_continuous(breaks = c(-0.1, 0, 0.1))
    } else {
      transmission_plot <- plot_R(
        setNames(list(job_EpiSewer_result[[i_select]]), target_select),
        forecast = FALSE, median = T, intervals = c(0.5, 0.95), seeding = TRUE
        ) +
        scale_y_continuous(breaks = target_R_breaks[[target_select]]) +
        coord_cartesian(xlim = date_lim, ylim = target_R_lim[[target_select]]) +
        ylab(expression(R[t]))
    }
    
    transmission_plot <- transmission_plot +
      theme(
        axis.title.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        text = element_text(family = fontfam),
        axis.text.y = element_text(angle = 90, hjust = 0.5)
        ) +
      scale_color_manual(values = color_select) +
      scale_fill_manual(values = color_select)
    
    concentration_plot <- style_x(concentration_plot)
    transmission_plot <- style_x(transmission_plot)
    
    if (wwtp_select_i > 1) {
      concentration_plot <- remove_y(concentration_plot)
      transmission_plot <- remove_y(transmission_plot)
    }
    
    mainplot <- cowplot::plot_grid(
        concentration_plot,
        NULL,
        transmission_plot + theme(legend.position = "none"),
        ncol = 1, align = "v", rel_heights = c(0.5, -0.02, 0.5)
        )
    
    if (wwtp_select_i == length(wwtps_select)) {
      target_strip <- cowplot::plot_grid(
        NULL,
        cowplot::get_plot_component(
          concentration_plot + 
        facet_grid(model ~ ., scales = "free_y") + 
        theme(
          strip.text.y = element_text(angle = -90),
          strip.background = element_rect(fill = NA, color = "black")
          ),
          pattern = "strip-r-1"),
        NULL, ncol = 1, rel_heights = c(0.025, 0.95, 0.09))
      
     mainplot <- cowplot::plot_grid(
        mainplot, target_strip, nrow = 1, rel_widths = c(0.9, 0.1)
        ) 
    }
    return(mainplot)
  })
  
if (wwtp_select_i == 1) {
  gridlabels <- c("A", "B", "C", "D")
} else {
  gridlabels <- NULL
}

if (!show_flow) {
  main_part <- cowplot::plot_grid(
  plotlist = main_plots, ncol = 1,
  labels = gridlabels[1:3]
  )
} else {
  main_part <- cowplot::plot_grid(
  plotlist = c(main_plots, list(flow_part)), ncol = 1, rel_heights = c(rep(0.27, 3), 0.19),
  labels = gridlabels
  )
}

if (wwtp_select_i == 1) {
  wwtp_strip_widths <- c(0.15, 0.82, 0.03) # first
} else if (wwtp_select_i == 3) {
  wwtp_strip_widths <- c(0.03, 0.85, 0.12) # last
} else {
  wwtp_strip_widths <- c(0.03, 0.94, 0.03)
}

wwtp_strip <- cowplot::plot_grid(
  NULL,
  cowplot::get_plot_component(
    flow_plot + 
      facet_grid(. ~ wwtp, scales = "free_x") + 
      theme(strip.background = element_rect(fill = NA, color = "black")),
    pattern = "strip-t-1"),
  NULL, nrow = 1, rel_widths = wwtp_strip_widths)

wwtp_panel <- cowplot::plot_grid(
  wwtp_strip, main_part, ncol = 1, rel_heights = c(0.03, 0.97), align = "v"
)

return(wwtp_panel)
})
))
}
```

#### Main figures
```{r, fig.width = 10, fig.height = 12}
wwtp_season_list <- list(
  list(
    season_select = "2022/23",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2023/24",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2024/25",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  #with growth rates
  list(
    season_select = "2022/23",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = TRUE,
    show_flow = FALSE
  ),
  list(
    season_select = "2023/24",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = TRUE,
    show_flow = FALSE
  ),
  list(
    season_select = "2024/25",
    wwtps_select = c(
      "Zurich" = "ARA Werdhoelzli",
      "Lugano" = "CDA Lugano",
      "Chur" = "ARA Chur"
      ),
    use_growth_rate = TRUE,
    show_flow = FALSE
  )
)

for (i in 1:length(wwtp_season_list)) {
  wwtp_panels <- get_wwtp_panels(
    season_select = wwtp_season_list[[i]]$season_select,
    wwtps_select = wwtp_season_list[[i]]$wwtps_select,
    use_growth_rate = wwtp_season_list[[i]]$use_growth_rate,
    show_flow = wwtp_season_list[[i]]$show_flow
    )
  overview_plot <- cowplot::plot_grid(plotlist = wwtp_panels, nrow = 1, rel_widths = c(0.357, 0.318, 0.338))
  
  if (wwtp_season_list[[i]]$use_growth_rate) {
    plotname <- paste0("main_overview_growth_rate_",stringr::str_replace(wwtp_season_list[[i]]$season_select,"/","-"),".pdf")
    ggsave(plot = overview_plot, here::here("figures", "overview", plotname), width = 10, height = 12*(1-0.19), scale = 0.9)
  } else {
    plotname <- paste0("main_overview_",stringr::str_replace(wwtp_season_list[[i]]$season_select,"/","-"),".pdf")
    ggsave(plot = overview_plot, here::here("figures", "overview", plotname), width = 10, height = 12, scale = 0.9)
  }
}
```

#### Additional figures
```{r fig.width = 10, fig.height = 9.72}
wwtp_season_list <- list(
  list(
    season_select = "2022/23",
    wwtps_select = c(
      "Geneva" = "STEP Aire",
      "Thal/Altenrhein" = "ARA Altenrhein",
      "Laupen/Sensetal" = "ARA Sensetal"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
    list(
    season_select = "2023/24",
    wwtps_select = c(
      "Geneva" = "STEP Aire",
      "Thal/Altenrhein" = "ARA Altenrhein",
      "Laupen/Sensetal" = "ARA Sensetal"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2023/24",
    wwtps_select = c(
      "Lausanne" = "STEP Vidy",
      "Bern" = "ARA Region Bern",
      "Basel" = "ARA Basel/Prorheno"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2023/24",
    wwtps_select = c(
      "Luzern" = "ARA Buholz",
      "Porrentruy" = "STEP Porrentruy",
      "Neuchatel" = "STEP Neuchatel"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2023/24",
    wwtps_select = c(
      "Zuchwil" = "ARA Zuchwil",
      "Schwyz" = "ARA Schwyz"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2024/25",
    wwtps_select = c(
      "Geneva" = "STEP Aire",
      "Thal/Altenrhein" = "ARA Altenrhein",
      "Laupen/Sensetal" = "ARA Sensetal"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2024/25",
    wwtps_select = c(
      "Lausanne" = "STEP Vidy",
      "Basel" = "ARA Basel/Prorheno"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  ),
  list(
    season_select = "2024/25",
    wwtps_select = c(
      "Luzern" = "ARA Buholz",
      "Neuchatel" = "STEP Neuchatel"
      ),
    use_growth_rate = FALSE,
    show_flow = TRUE
  )
)
  
for (i in 1:length(wwtp_season_list)) {
  try({
    wwtp_panels <- get_wwtp_panels(
    season_select = wwtp_season_list[[i]]$season_select,
    wwtps_select = wwtp_season_list[[i]]$wwtps_select,
    use_growth_rate = wwtp_season_list[[i]]$use_growth_rate,
    show_flow = wwtp_season_list[[i]]$show_flow
    )
  overview_plot <- cowplot::plot_grid(plotlist = wwtp_panels, nrow = 1, rel_widths = c(0.357, 0.318, 0.338))
  plotname <- stringr::str_replace_all(paste0("overview_",paste(names(wwtp_season_list[[i]]$wwtps_select), collapse = "-"),"_",wwtp_season_list[[i]]$season_select,".pdf"),"/","-")
  print(plotname)
  ggsave(plot = overview_plot, here::here("figures", "overview", plotname), width = 10, height = 12, scale = 0.9)
  })
}
```
