## Setup
```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```
```{r}
library(targets)
library(dplyr)
library(EpiSewer)
library(ggplot2)
library(ggpattern)
library(data.table)
library(scoringutils)
source("code/pipeline/utils_pipeline.R")
source("code/utils_postprocess.R")
source("code/pipeline/utils_real_time.R")
source("data/assumptions/epi_params_EpiSewer-study.R")
source("code/local_config.R")
```

Create pipeline folders if they do not exist
```{r}
create_real_time_pipelines("_real_time_selection_targets_22-23")
create_real_time_pipelines("_real_time_selection_targets_23-24")
create_real_time_pipelines("_real_time_selection_targets_24-25") 
```

## Run pipelines

```{r}
create_real_time_pipelines("_real_time_selection_targets_22-23") 
all_pipelines <- paste0("_real_time_", names(all_selection_targets))
print(paste("Running", length(names(all_selection_targets)), "pipelines"))

for (selection_to_run in all_pipelines) {
  run_pipeline(targets_proj_name = selection_to_run, submit = TRUE)
  if(length(tar_read(jobs_EpiSewer_invalid))>0) {
    warning("There are invalid jobs.")
  }
}
```
```{r}
create_real_time_pipelines("_real_time_selection_targets_23-24") 
all_pipelines <- paste0("_real_time_", names(all_selection_targets))
print(paste("Running", length(names(all_selection_targets)), "pipelines"))

for (selection_to_run in all_pipelines) {
  run_pipeline(targets_proj_name = selection_to_run, submit = TRUE)
  if(length(tar_read(jobs_EpiSewer_invalid))>0) {
    warning("There are invalid jobs.")
  }
}
```

```{r}
create_real_time_pipelines("_real_time_selection_targets_24-25") 
all_pipelines <- paste0("_real_time_", names(all_selection_targets))
print(paste("Running", length(names(all_selection_targets)), "pipelines"))

for (selection_to_run in all_pipelines) {
  run_pipeline(targets_proj_name = selection_to_run, submit = TRUE)
  if(length(tar_read(jobs_EpiSewer_invalid))>0) {
    warning("There are invalid jobs.")
  }
}
```

Check all results
```{r}
all_pipelines <- purrr::list_c(lapply(c("_real_time_selection_targets_22-23","_real_time_selection_targets_23-24","_real_time_selection_targets_24-25"), function(x) {
  source(paste0("pipelines/", x, ".R"))
  paste0("_real_time_", names(all_selection_targets))
}))
```

```{r}
rbindlist(lapply(all_pipelines, function(pipeline) {
  suppressMessages(setup_pipeline(pipeline))
  return(tar_read(job_EpiSewer_submission) |>
    mutate(total = 1, .before = exists) |>
    summarise(across(total:submitted, \(x) sum(x, na.rm = T))) |> 
    mutate(pipeline = pipeline, .before = total)
    )
}), fill = TRUE)
```

## Load results
```{r}
all_pipelines <- purrr::list_c(lapply(c("_real_time_selection_targets_22-23","_real_time_selection_targets_23-24","_real_time_selection_targets_24-25"), function(x) {
  source(paste0("pipelines/", x, ".R"))
  paste0("_real_time_", names(all_selection_targets))
}))
```

```{r}
job_EpiSewer_result <- load_EpiSewer_results(all_pipelines)
data_PCR_agg_select <- get_data_PCR_agg_select(all_pipelines)
data_flow_select <- get_data_flow_select(all_pipelines)
```

Build index
```{r}
get_season <- function(date) {
  if (date > as.Date("2022-08-01") & date <= as.Date("2023-08-01")) {
    return("2022/23")
  } else if (date > as.Date("2023-08-01") & date <= as.Date("2024-08-01")) {
    return("2023/24")
  } else if (date > as.Date("2024-08-01") & date <= as.Date("2025-08-01")) {
    return("2024/25")
  } else {
    return("unknown")
  }
}

results_index <- bind_rows(lapply(job_EpiSewer_result, function(x) {
  if (length(x) == 0) { data.frame(wwtp = NA, target = NA, estimation_date = NA, season = NA, R_model = NA)
  } else {
    return(data.frame(
      wwtp = x$job$selection$wwtp,
      target = x$job$selection$target,
      estimation_date = lubridate::as_date(x$job$selection$date_select[[1]]["to"]),
      season = sapply(lubridate::as_date(x$job$selection$date_select[[1]]["to"]), get_season),
      R_model = x$job$selection$module_infections
  ))}
  }))
rownames(results_index) <- NULL
results_index$i <- 1:nrow(results_index)

get_result_label <- function(x) {
  paste(
    x$summary$R[type == "estimate", max(date)],
    x$job$selection$wwtp,
    x$job$selection$target,
    x$job$selection$season,
    x$job$selection$module_infections
    )
}

get_result_label_minimal <- function(x) {
  paste(
    x$job$selection$wwtp,
    x$job$selection$target,
    paste("Estimation date:", x$summary$R[type == "estimate", max(date)]),
    sep = " | "
    )
}
```

## Preparation

```{r}
palette_targets <- c("#BC3C29FF","#0072B5FF","#E18727FF")
```

### Select season
In the following, the season and wwtps for which to compute performance scores are selected
```{r}
wwtps_select <- c("Zurich" = "ARA Werdhoelzli", "Lugano" = "CDA Lugano", "Chur" = "ARA Chur")
season_select <- "2023/24"
selection <- list(
  list(wwtp_select = wwtps_select[1], target_select = "SARS-N2", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[1], target_select = "IAV-M", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[1], target_select = "RSV-N", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[2], target_select = "SARS-N2", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[2], target_select = "IAV-M", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[2], target_select = "RSV-N", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[3], target_select = "SARS-N2", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[3], target_select = "IAV-M", season_select = season_select, R_model_select = "R_gp"),
  list(wwtp_select = wwtps_select[3], target_select = "RSV-N", season_select = season_select, R_model_select = "R_gp")
)

results_select_list <- lapply(selection, function(x) {
  res <- results_index |> filter(wwtp == x$wwtp_select, target == x$target_select, season == x$season_select, R_model == x$R_model_select)
  if (nrow(res)==0) {
    stop(x)
  }
  res |> filter(estimation_date != max(estimation_date, na.rm = T))
})

baseline_select_list <- lapply(selection, function(x) {
  results_index |> filter(wwtp == x$wwtp_select, target == x$target_select, season == x$season_select, R_model == x$R_model_select) |> slice_max(estimation_date)
})
```

### Load wave dates
```{r}
wave_dates <- readr::read_csv(here::here("data", "assumptions", "wave_dates.csv"))

start_date_list <- lapply(baseline_select_list, function(baseline_select) {
  wave_dates |> filter(wwtp == baseline_select$wwtp[1], target == baseline_select$target[1], season == baseline_select$season[1]) |> pull(start_date)
})

end_date_list <- lapply(baseline_select_list, function(baseline_select) {
  wave_dates |> filter(wwtp == baseline_select$wwtp[1], target == baseline_select$target[1], season == baseline_select$season[1]) |> pull(end_date)
})
```

### Infection trends
```{r}
infections_trend_list <- lapply(baseline_select_list, function(baseline_select) {
  R_baseline <- job_EpiSewer_result[[baseline_select$i]]$summary$R[seeding == FALSE & type=="estimate",]
  setorderv(R_baseline, cols = "date")
  R_baseline[, R_value := median]
  R_baseline[, infection_trend_type := ifelse(R_value > 1, "increasing", "decreasing")]
  R_baseline[, wwtp := baseline_select$wwtp[1]]
  R_baseline[, target := baseline_select$target[1]]
  return(R_baseline[, c("wwtp", "target", "date", "R_value", "infection_trend_type")])
})
```

```{r}
rbindlist(infections_trend_list) |> 
  filter(!is.na(R_value)) |> 
  ggplot(aes(x=date, y=R_value)) + 
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_point(aes(color = infection_trend_type)) + 
  scale_x_date(date_labels = "%m\n%y") +
  facet_grid(wwtp~target, scales = "free_y") +
  theme_bw() + theme(legend.position = "top")
```

## Results
### Detected outliers
```{r}
detected_outliers <- lapply(baseline_select_list, function(baseline_select) {
  if (nrow(baseline_select) == 0 || is.null(job_EpiSewer_result[[baseline_select$i]]$summary$outliers)) {
    return(NULL)
  }
  outlier_df <- job_EpiSewer_result[[baseline_select$i]]$summary$outliers[epsilon > 1, "date"]
  outlier_df[ , wwtp := baseline_select$wwtp[1]]
  outlier_df[ , target := baseline_select$target[1]]
  outlier_df[ , outlier_detected := TRUE]
  data.table::setcolorder(outlier_df, c("wwtp", "target", "date", "outlier_detected"))
  return(outlier_df)
})
```

### Catchment population sizes
```{r}
wwtps <- readr::read_csv(
  here::here("data", "data merging", "wwtp_info.csv"),
  show_col_types = FALSE
) %>%
  select(name, ara_id, population)

wwtps |> filter(name %in% unique(sapply(baseline_select_list, function(x) x$wwtp))) |> select(name, population)
```

### Real-time R coverage

```{r}
R_real_time_list <- get_R_median_real_time_list(results_select_list, baseline_select_list)
```

```{r}
R_coverage <- rbindlist(lapply(1:length(baseline_select_list), function(i) {
  results_select <- results_select_list[[i]]
  baseline_select <- baseline_select_list[[i]]
  return(R_real_time_list[[i]][
      date >= start_date_list[[i]] & 
      estimation_date > start_date_list[[i]] &
      date <= end_date_list[[i]], 
    .(
      wwtp = baseline_select$wwtp,
      target = baseline_select$target,
      coverage = within
    ), 
    by = c("date", "estimation_date", "h")])
}))
```

```{r fig.width = 3, fig.height = 5}
R_coverage_week <- R_coverage[, h_week := (-as.numeric(h) %/% 7)][h<=14 & h >= -9*7, .(coverage = sum(coverage<0.95, na.rm = T)/sum(!is.na(coverage))), by = c("wwtp", "target", "h_week")]

target_shedding_windows <- data.frame(
  target = as.character(unique(R_coverage_week$target))
) |> mutate(
  window_q90 = sapply(target, function(x) (which(cumsum(get_shedding_dist(x))>=0.9)[1]-1) + 0*(which(cumsum(get_generation_dist(x))>=0.9)[1])),
  window_q90_week = window_q90 / 7,
  y = 0.80-c(0.05, 0.05, 0.05), angle = c(90, 90, 90), vjust = c(0, 0, 0), hjust = c(0, 0, 0),
  target = factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  )

R_coverage_week[
  , target := factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  ][
  , wwtp := factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T)
  ]

consistency_plot <- R_coverage_week |> 
  ggplot(aes(x=h_week)) +
  geom_vline(xintercept = 0, linetype = "solid", color = "grey") +
  geom_vline(data = target_shedding_windows, aes(xintercept = window_q90_week, color = target), linetype = "dashed", show.legend = FALSE) +
  geom_text(data = target_shedding_windows |> mutate(wwtp := factor("ARA Chur", levels = wwtps_select, labels = names(wwtps_select), ordered = T)), aes(x = window_q90_week, color = target, label = paste(target), y = y, angle = angle, vjust = vjust, hjust = hjust),
           size = 2.5, nudge_x = -0.08, nudge_y = 0.02, show.legend = FALSE
            ) +
  geom_line(aes(y=coverage, color = target)) +
  geom_point(aes(y=coverage, color = target)) +
  theme_bw() +
  facet_grid(wwtp ~ .) +
  theme(
    legend.position = "top",
    strip.background = element_rect(fill = "white"),
    panel.grid.minor = element_blank()
    ) +
  xlab("Real-time lag [weeks]") + 
  ylab(expression(Retrospective~R[t]~coverage)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = expansion(add = c(0.04, 0.01))) +
  scale_x_reverse(breaks = seq(-2,20), expand = expansion(add = c(0, 0.2))) + xlim(c(9,-0.1)) +
  coord_cartesian(ylim = c(0.80, 1), xlim = c(8.4, -0.1)) +
  scale_color_manual(name = "Pathogen", values = palette_targets) +
  guides(color = guide_legend())
consistency_plot
```

### Real-time error of median Rt

```{r}
R_real_time_error_list <- get_R_median_error_real_time_list(results_select_list, baseline_select_list)
```

```{r}
R_median_error <- rbindlist(lapply(1:length(baseline_select_list), function(i) {
  results_select <- results_select_list[[i]]
  baseline_select <- baseline_select_list[[i]]
  return(R_real_time_error_list[[i]][
      date >= start_date_list[[i]] & 
      estimation_date > start_date_list[[i]] &
      date <= end_date_list[[i]], 
    .(
      wwtp = baseline_select$wwtp,
      target = baseline_select$target,
      MAE = mean(abs(median_error))
    ), 
    by = "h"])
}))
```

```{r fig.width = 5, fig.height = 3}
R_median_error_week <- R_median_error[, h_week := (-as.numeric(h) %/% 7)][h<=14 & h >= -9*7, .(MAE = mean(MAE, na.rm = T)), by = c("wwtp", "target", "h_week")]

target_shedding_windows <- data.frame(
  target = as.character(unique(R_median_error_week$target))
) |> mutate(
  window_q90 = sapply(target, function(x) (which(cumsum(get_shedding_dist(x))>=0.9)[1]-1) + 0*(which(cumsum(get_generation_dist(x))>=0.9)[1])),
  window_q90_week = window_q90 / 7,
  y = 0.35-c(0.05, 0.05, 0.05), angle = c(90, 90, 90), vjust = c(0, 0, 0), hjust = c(1, 1, 1),
  target = factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  )

R_median_error_week[
  , target := factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  ][
  , wwtp := factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T)
  ]

median_error_plot <- R_median_error_week |> 
  ggplot(aes(x=h_week)) +
  geom_vline(xintercept = 0, linetype = "solid", color = "grey") +
  geom_vline(data = target_shedding_windows, aes(xintercept = window_q90_week, color = target), linetype = "dashed", show.legend = FALSE) +
  geom_text(data = target_shedding_windows |> mutate(wwtp := factor("ARA Werdhoelzli", levels = wwtps_select, labels = names(wwtps_select), ordered = T)), aes(x = window_q90_week, color = target, label = paste(target), y = y, angle = angle, vjust = vjust, hjust = hjust),
           size = 2.5, nudge_x = -0.08, nudge_y = 0.02, show.legend = FALSE
            ) +
  geom_line(aes(y=MAE, color = target)) +
  geom_point(aes(y=MAE, color = target)) +
  theme_bw() +
  facet_grid(. ~ wwtp) +
  theme(
    legend.position = "top",
    strip.background = element_rect(fill = "white"),
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
    ) +
  xlab("Real-time lag [weeks]") + 
  ylab(expression(Retrospective~MAE~of~median~R[t])) +
  scale_x_reverse(breaks = seq(-2,20), expand = expansion(add = c(0, 0.2))) + xlim(c(9,-0.1)) +
  coord_cartesian(ylim = c(NA, NA), xlim = c(8.4, -0.1)) +
  scale_color_manual(name = "Pathogen", values = palette_targets) +
  guides(color = guide_legend())
median_error_plot

ggsave(median_error_plot, filename = here::here("figures", "real_time", paste0("MAE_Rt_median_",stringr::str_replace(season_select,"/","-"),".pdf")), width = 10, height = 3)
```
### Forecast performance 

#### Preparation

Forecast horizon to be evaluated
```{r}
horizon_selection <- 14
```

```{r}
ground_truth_list <- mapply(function(baseline_select, detected_outliers_df) {
  ground_truth <- merge(
    data_PCR_agg_select[[baseline_select$i[1]]][, c("date", "gc_per_mlww")],
    data_flow_select[[baseline_select$i[1]]][, c("date", "flow")]
  )
  ground_truth[, conc_normalized := gc_per_mlww * flow]
  ground_truth <- ground_truth[!(date %in% detected_outliers_df[, date]),] # remove outliers from evaluation
  return(ground_truth)
}, baseline_select = baseline_select_list, detected_outliers_df = detected_outliers, SIMPLIFY = FALSE)
```

```{r}
# note that scoringutils will give an irrelevant warning that there is no model column in the data - the forecasts are correctly stratified
all_forecasts_list <- get_forecasts_list(results_select_list, baseline_select_list, ground_truth_list)
all_baseline_list <- get_baseline_list(baseline_select_list, ground_truth_list, all_forecasts_list)
```

```{r}
metrics_list <- list(
  "wis" = wis, 
  "overprediction" = overprediction_quantile,
  "underprediction" = underprediction_quantile,
  "dispersion" = dispersion_quantile,
  "bias" = bias_quantile,
  "interval_coverage_50" = purrr::partial(interval_coverage, interval_range = 50),
  "interval_coverage_90" = purrr::partial(interval_coverage, interval_range = 90),
  "interval_coverage_deviation" = interval_coverage_deviation
)
conc_score_list <- lapply(all_forecasts_list, function(all_forecasts) score(all_forecasts, metrics = metrics_list))
baseline_score_list <- lapply(all_baseline_list, function(all_baseline) score(all_baseline, metrics = metrics_list))
```

#### Forecast bias

Infections increasing vs decreasing
```{r}
conc_score_total_agg_list <- lapply(1:length(conc_score_list), function(i) {
  start_date <- start_date_list[[i]]
  end_date <- end_date_list[[i]]
  conc_score_agg <- merge(conc_score_list[[i]], infections_trend_list[[i]], by.x = c("wwtp","target","estimation_date"), by.y = c("wwtp","target","date"))
  return(conc_score_agg[
    estimation_date >= (start_date) & estimation_date <= (end_date) & h <= horizon_selection,
    .(bias = mean(bias, na.rm = T)),
    by = c("wwtp","target","infection_trend_type","estimation_date")
    ][,.(bias = mean(bias, na.rm = T)),by = c("wwtp","target","infection_trend_type")])
})

bias_plot_data <- rbindlist(conc_score_total_agg_list)[
  , target := factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  ][
  , wwtp := factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T)
  ][
  , infection_trend_type := factor(infection_trend_type, levels = c("increasing", "decreasing"))
  ]

bias_plot_data[, wwtp := factor(wwtp)]
bias_plot_data[, target := factor(target)]
bias_plot_data[, infection_trend_type := factor(infection_trend_type)]
bias_plot_data[, nudge_y := -(as.numeric(infection_trend_type)+2*(as.numeric(target)-1)-(6/2+0.5))*0.15]

bias_plot <- bias_plot_data |> 
  ggplot(aes(x=bias, y=wwtp)) +
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_point(aes(shape = infection_trend_type, color = target), size = 3, position = position_nudge(y = bias_plot_data$nudge_y)) +
  coord_cartesian(xlim = c(-1,1)) +
  facet_grid(wwtp ~ ., scales = "free_y") +
  scale_color_manual(name = "Pathogen", values = palette_targets) +
  scale_shape_manual(name = "Infection trend", values = c(17, 19)) +
  theme_bw() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.01, 0.99),
    legend.justification = c("left", "top"),
    legend.background = element_blank(),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    strip.background = element_rect(fill = "white"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank()
    ) +
  xlab("Forecast bias") + ylab(" ") +
  guides(shape = guide_legend(), color = guide_none())

bias_plot
```

#### Interval coverage

```{r}
coverage_data <- rbindlist(lapply(1:length(all_forecasts_list), function(i) {
  all_forecasts <- all_forecasts_list[[i]]
  all_forecasts <- all_forecasts[quantile_level %in% c(0.005, round(seq(0, 1, by = 0.05),3), 0.995),]
  start_date <- start_date_list[[i]]
  end_date <- end_date_list[[i]]
  tryCatch(get_coverage(
  all_forecasts[h <= horizon_selection & estimation_date >= start_date & estimation_date <= end_date 
                  ,][
  , target := factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T)
  ][
  , wwtp := factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T)
  ], by = c("wwtp", "target")
  ), error = function(e) return(data.table()))}
))

coverage_plot <- ggplot(coverage_data, aes(x = interval_range, y = interval_coverage*100, color = target)) +
  geom_polygon(data = data.frame(x = c(0, 0, 100), y = c(0, 100, 100), g = c("o", "o", "o"), stringsAsFactors = TRUE),
                 aes(x = x, y = y), alpha = 0.15,
                 colour = "white", fill = "grey") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "grey") +
  geom_line(aes(group = target)) +
  facet_wrap(~wwtp, ncol = 1) +
  theme_bw() +
  facet_grid(wwtp ~ .) +
  theme(
    legend.position = "top",
    strip.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
    ) +
  scale_color_manual(name="Pathogen", values = palette_targets) +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1, scale = 1)) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1, scale = 1)) +
  ylab("% of observations covered") + xlab("Forecast interval") +
  coord_cartesian(expand = FALSE, ylim = c(-5,105))

coverage_plot
```

### Forecast plot
```{r fig.width = 10, fig.height = 5}
if (season_select == "2023/24") {
  example_i <- 3

base_data <- data_PCR_agg_select[[baseline_select_list[[example_i]]$i]]
base_flow <- data_flow_select[[baseline_select_list[[example_i]]$i]]
base_res <- job_EpiSewer_result[[baseline_select_list[[example_i]]$i]]

dates_show <- results_select_list[[example_i]] |> 
  mutate(
    year = lubridate::year(estimation_date),
    month = lubridate::month(estimation_date)
    ) |> 
  filter(estimation_date >= "2023-12-01", estimation_date < "2024-04-01") |> 
  group_by(year, month) |> 
  slice_min(estimation_date) |> 
  pull(estimation_date)

dates_show <- as.Date(c("2023-11-26","2024-01-02","2024-02-11"))

res <- job_EpiSewer_result[results_select_list[[example_i]] |> filter(estimation_date %in% dates_show) |> pull(i)]
names(res) <- paste0(format(dates_show, "%d %b, %Y"), ", Zurich")

conc_plot <- plot_concentration(
  res,
  measurements = base_data,
  flows = base_flow,
  concentration_col = "gc_per_mlww",
  normalized = TRUE,
  median = TRUE,
  date_margin_right = 300,
  facet_model = T,
  facet_direction = "cols",
  obs_size = 1, obs_shape = 20, obs_forecast_shape = 8
  ) + 
  coord_cartesian(ylim = c(0,75), xlim = as.Date(c("2023-10-20", "2024-03-15"))) +
  scale_color_manual(values = rep("#E18727FF", 3)) +
  scale_fill_manual(values = rep("#E18727FF", 3)) +
  scale_x_date(date_breaks = "1 months", date_labels = "%b '%y") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  ylab(expression(C[t]^plain("norm")~plain("[gc/mL]"))) +
  geom_text(
    data = data.frame(
      date=as.Date(c("2023-10-26", "2024-02-01","2024-02-23")),
      y = c(40, 65, 50),
      text = c("Outlier", "Peak\nin infections", "Decline"),
      model = forcats::fct_inorder(c("26 Nov, 2023, Zurich", "02 Jan, 2024, Zurich", "11 Feb, 2024, Zurich"))
      ), aes(x=date, y=y, label=text), size = 3, color = "red", hjust = 0, lineheight = 0.9) +
  geom_segment(
    data = data.frame(
      x = as.Date(c("2023-11-08", "2024-01-28", "2024-03-02")),
      xend = as.Date(c("2023-11-21", "2024-01-12", "2024-02-19")),
      y = c(50, 60, 40),
      yend = c(75, 40, 20),
      model = forcats::fct_inorder(c("26 Nov, 2023, Zurich", "02 Jan, 2024, Zurich", "11 Feb, 2024, Zurich"))
      ), aes(x=x, xend=xend, y=y, yend=yend), color = "red", size = 0.5,
    arrow = grid::arrow(length = grid::unit(0.05, "inches")))
    

R_plot <- plot_R(
  c(res, list(baseline = base_res)),
  date_margin_right = 300,
  facet_model = T,
  median = TRUE,
  facet_direction = "cols",
  base_model = "baseline"
  ) + 
  coord_cartesian(ylim = c(0.6,1.8), xlim = as.Date(c("2023-10-20", "2024-03-15"))) +
  scale_color_manual(values = rep("#E18727FF", 3)) +
  scale_fill_manual(values = rep("#E18727FF", 3)) +
  scale_x_date(date_breaks = "1 months", date_labels = "%b '%y") +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  ) +
  ylab(expression(R[t]))

forecast_plot <- cowplot::plot_grid(
  conc_plot, NULL, R_plot,
  ncol = 1, align = "v",
  labels = c("A", ""),
  rel_heights = c(0.49, -0.02, 0.51)
)

forecast_plot
}
```

### Combined figure
```{r fig.width = 10, fig.height = 9}
combined_legend <- cowplot::plot_grid(
  cowplot::get_plot_component(consistency_plot, pattern = "guide-box-top"),
  nrow = 1
  )

if (season_select == "2023/24") {
  combined_fig <- cowplot::plot_grid(
  combined_legend,
  forecast_plot,
  NULL,
  cowplot::plot_grid(
    consistency_plot + theme(legend.position = "none"),
    bias_plot,
    coverage_plot + theme(legend.position = "none"),
    nrow = 1, labels = c("B", "C", "D"), align = "h",
    axis = "tb", rel_widths = c(1, 0.9, 1)),
  ncol = 1, rel_heights = c(0.05, 0.4, 0.01, 0.61), align = "v"
)
combined_fig
  
  ggsave(combined_fig, filename = here::here("figures", "real_time", paste0("combined_performance_all_",stringr::str_replace(season_select,"/","-"),".pdf")), width = 10, height = 9, scale = 0.9)
} else if (season_select %in% c("2022/23", "2024/25")) {
  combined_fig <- cowplot::plot_grid(
  combined_legend,
  cowplot::plot_grid(
    consistency_plot + theme(legend.position = "none"),
    bias_plot,
    coverage_plot + theme(legend.position = "none"),
    nrow = 1, labels = c("A", "B", "C"), align = "h",
    axis = "tb", rel_widths = c(1, 0.9, 1)),
  ncol = 1, rel_heights = c(0.09, 0.91), align = "v"
)
  combined_fig
  
  ggsave(combined_fig, filename = here::here("figures", "real_time", paste0("combined_performance_all_",stringr::str_replace(season_select,"/","-"),".pdf")), width = 10, height = 6, scale = 0.9)
}
```

## Diagnostics
```{r}
total_draws <- 4*2500 # four chains with 2500 sampling iterations each

diagnostics_index <- cbind(results_index, rbindlist(lapply(job_EpiSewer_result, function(res){
  n_chains <- res$job$fit_opts$sampler$chains
  runtime <- ifelse("total" %in% names(res$runtime), res$runtime$total, NA)
  num_divergent <- ifelse("num_divergent" %in% names(res$diagnostics), sum(res$diagnostics$num_divergent), NA)
  num_divergent_max <- ifelse("num_divergent" %in% names(res$diagnostics), max(res$diagnostics$num_divergent), NA)
  min_ebfmi <- ifelse("ebfmi" %in% names(res$diagnostics), min(res$diagnostics$ebfmi), NA)
  num_max_treedepth <- ifelse("num_max_treedepth" %in% names(res$diagnostics), sum(res$diagnostics$num_max_treedepth), NA)
  if ("R_diagnostics" %in% names(res$summary)) {
      mean_rhat <- res$summary$R_diagnostics[seeding == FALSE, mean(rhat, na.rm = T)]
      share_rhat <- res$summary$R_diagnostics[seeding == FALSE, sum(rhat > 1.05)/.N]
      mean_ess_bulk <- res$summary$R_diagnostics[seeding == FALSE, mean(ess_bulk, na.rm = T)]
      mean_ess_tail <- res$summary$R_diagnostics[seeding == FALSE, mean(ess_tail, na.rm = T)]
      share_ess_bulk <- res$summary$R_diagnostics[seeding == FALSE, sum(ess_bulk < n_chains*100)/.N]
      share_ess_tail <- res$summary$R_diagnostics[seeding == FALSE, sum(ess_tail < n_chains*100)/.N]
  } else {
    mean_rhat <- NA
    share_rhat <- NA
    mean_ess_bulk <- NA
    mean_ess_tail <- NA
    share_ess_bulk <- NA
    share_ess_tail <- NA
  }
  data.frame(
    runtime = runtime,
    num_divergent = num_divergent,
    num_divergent_max = num_divergent_max,
    min_ebfmi = min_ebfmi,
    num_max_treedepth = num_max_treedepth,
    mean_rhat = mean_rhat,
    share_rhat = share_rhat,
    mean_ess_bulk = mean_ess_bulk,
    mean_ess_tail = mean_ess_tail,
    share_ess_bulk = share_ess_bulk,
    share_ess_tail = share_ess_tail
    )
})))
diagnostics_index <- diagnostics_index |> mutate(
  target = factor(target, levels = c("SARS-N2", "IAV-M", "RSV-N"), labels = c("SARS-CoV-2", "IAV", "RSV"), ordered = T),
  wwtp = factor(wwtp, levels = wwtps_select, labels = names(wwtps_select), ordered = T)
)
```

```{r}
diagnostics_theme_ts <- function(p) {
  p + geom_point(shape = 4) +
  facet_grid(target~wwtp) +
  scale_x_date(date_breaks = "4 months", date_labels = "%m\n%y") +
  theme_bw() +
  theme(
    legend.position = "top",
    strip.background = element_rect(fill = "white")
    ) +
  xlab("Estimation date") +
  scale_color_manual(name = "Pathogen", values = palette_targets)
}

diagnostics_theme_bp <- function(p) {
  p +
  facet_grid(target~wwtp) +
  theme_bw() +
  theme(
    legend.position = "top",
    strip.background = element_rect(fill = "white")
    ) +
  xlab("Season") +
  scale_color_manual(name = "Pathogen", values = palette_targets)
}
```


#### Divergent transitions
```{r}
diagnostics_theme_bp(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = season, y = num_divergent/total_draws, color = target)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    geom_boxplot() +
   ylab("Divergent transitions") +
   coord_cartesian(ylim = c(0, 0.5))
)

diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = num_divergent/total_draws, color = target)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.6,0.2)) +
    ylab("Divergent transitions") + 
    coord_cartesian(ylim = c(0, 0.5))
  )

ggsave(here::here("figures", "real_time", "diagnostics_divergent_transitions.pdf"), width = 10, height = 5)
```

#### EBFMI
The EBFMI should be > 0.2 for all chains.
```{r}
diagnostics_theme_bp(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = season, y = min_ebfmi, color = target)) +
   geom_hline(yintercept = 0.2, linetype = "dashed") +
    geom_boxplot() +
   ylab("Smallest E-BFMI") 
)

diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = min_ebfmi, color = target)) +
    geom_hline(yintercept = 0.2, linetype = "dashed") +
    ylab("Smallest E-BFMI")
)

ggsave(here::here("figures", "real_time", "diagnostics_ebfmi.pdf"), width = 10, height = 5)
```

#### Maximum treedepth events
```{r}
diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = num_max_treedepth/total_draws, color = target)) +
    geom_hline(yintercept = 0.01, linetype = "dashed") +
    ylab("Maximum treedepth events") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    coord_cartesian(ylim = c(0, 0.05))
)
```

#### Rhat
Share of dates with Rhat>1.05
```{r}
diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = share_rhat, color = target)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    ylab("R-hat > 1.05") +
    coord_cartesian(ylim = c(0, 1))
)

diagnostics_theme_bp(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = season, y = 1-share_rhat, color = target)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    geom_boxplot() +
    ylab("R-hat < 1.05")
)

diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = mean_rhat, color = target)) +
    geom_hline(yintercept = 1.05, linetype = "dashed") +
    ylab("R-hat") + coord_cartesian(ylim = c(NA, 1.14))
)

ggsave(here::here("figures", "real_time", "diagnostics_rhat.pdf"), width = 10, height = 5)
```

#### Bulk ESS
```{r}
diagnostics_theme_bp(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = season, y = mean_ess_bulk, color = target)) +
    geom_hline(yintercept = 400, linetype = "dashed") +
    geom_boxplot() +
    ylab("Effective sample size (bulk)")
)

diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = mean_ess_bulk, color = target)) +
    ylab("Effective sample size (bulk)") +
    geom_hline(yintercept = 400, linetype = "dashed") +
    coord_cartesian(ylim = c(0, 6000))
)

ggsave(here::here("figures", "real_time", "diagnostics_ess_bulk.pdf"), width = 10, height = 5)
```

#### Tail ESS
```{r}
diagnostics_theme_bp(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = season, y = mean_ess_tail, color = target)) +
    geom_hline(yintercept = 400, linetype = "dashed") +
    geom_boxplot() +
    ylab("Effective sample size (tail)")
)

diagnostics_theme_ts(
  diagnostics_index |> filter(!is.na(target)) |> 
    ggplot(aes(x = estimation_date, y = mean_ess_tail, color = target)) +
    ylab("Effective sample size (tail)") +
    geom_hline(yintercept = 400, linetype = "dashed")
)

ggsave(here::here("figures", "real_time", "diagnostics_ess_tail.pdf"), width = 10, height = 5)
```
