```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```
```{r}
library(targets)
library(dplyr)
library(EpiSewer)
library(ggplot2)
source("code/pipeline/utils_pipeline.R")
source("code/pipeline/utils_real_time.R")
source("data/assumptions/epi_params_EpiSewer-study.R")
source("code/local_config.R")
```

Create pipeline folders if they do not exist
```{r}
setup_pipeline("_subsampling")
```

## Run pipelines

This will run both EpiSewer and estimateR
```{r, include = FALSE}
run_pipeline(targets_proj_name = "_subsampling", submit = T)
if(length(tar_read(jobs_EpiSewer_invalid))>0) {
  warning("There are invalid jobs.")
}
```

Check results
```{r}
tar_load(job_EpiSewer_submission)

job_EpiSewer_submission |>
  mutate(total = 1, .before = exists) |>
  summarise(across(total:submitted, sum, na.rm = T))

tar_load(job_estimateR_submission)

job_estimateR_submission |>
  mutate(total = 1, .before = exists) |>
  summarise(across(total:submitted, sum, na.rm = T))
```

## Load results
```{r}
setup_pipeline("_subsampling")
tar_load(job_EpiSewer_result)
tar_load(job_estimateR_result)
```

Here we have to do some post-processing to make the results comparable:
estimateR does not provide results in the same structure as EpiSewer, and it does not provide
50% uncertainty intervals. Therefore, we remove the 50% intervals for both estimateR and EpiSewer
```{r}
for (i in seq_along(job_estimateR_result)) {
  try(job_estimateR_result[[i]]$summary$R <- job_estimateR_result[[i]]$summary$R |> rename(lower_0.95 = lower_outer, lower_0.5 = lower_inner, upper_0.5 = upper_inner, upper_0.95 = upper_outer))
  try(job_estimateR_result[[i]]$summary$R <- job_estimateR_result[[i]]$summary$R |> mutate(type = "estimate"))
  try(job_estimateR_result[[i]]$summary$R <- job_estimateR_result[[i]]$summary$R |> mutate(seeding = FALSE))
  try(job_estimateR_result[[i]]$summary$R <- job_estimateR_result[[i]]$summary$R |> mutate(median = mean))
  try(job_estimateR_result[[i]]$summary$R <- job_estimateR_result[[i]]$summary$R |> mutate(lower_0.5 = mean, upper_0.5 = mean))
  setDT(job_estimateR_result[[i]]$summary$R)
}

for (i in seq_along(job_EpiSewer_result)) {
  if (is.null(job_EpiSewer_result[[i]]$summary$R)) {
    next
  }
  try(job_EpiSewer_result[[i]]$summary$R[, lower_0.5 := median])
  try(job_EpiSewer_result[[i]]$summary$R[, upper_0.5 := median])
}
```

```{r}
tar_load(data_PCR_agg_select)
```

```{r}
tar_load(subsampling)
```

### Overall performance

```{r}
palette_targets <- c("SARS-CoV-2" = "#BC3C29FF", "IAV" = "#0072B5FF", "RSV" = "#E18727FF")
target_labels <- list(
  `SARS-N2` = "SARS-CoV-2",
  `IAV-M` = "IAV",
  `RSV-N` = "RSV"
)
palette_approaches <- c("EpiSewer" = "#1f407a", "estimateR" = "#20854EFF")
```

```{r}
R_results_all_EpiSewer <- rbindlist(lapply(job_EpiSewer_result, function(x) {
  R_result <- x$summary$R
  R_result[, wwtp := x$job$selection$wwtp]
  R_result[, target := x$job$selection$target]
  R_result[, subsampling_type := x$job$selection$subsampling[[1]]$type]
  R_result[, subsampling_subtype := x$job$selection$subsampling[[1]]$subtype]
  return(R_result)
}))
R_results_all_EpiSewer[, approach := "EpiSewer"]

R_results_all_estimateR <- rbindlist(lapply(job_estimateR_result, function(x) {
  R_result <- x$summary$R
  setDT(R_result)
  R_result[, wwtp := x$job$selection$wwtp]
  R_result[, target := x$job$selection$target]
  R_result[, subsampling_type := x$job$selection$subsampling[[1]]$type]
  R_result[, subsampling_subtype := x$job$selection$subsampling[[1]]$subtype]
  return(R_result)
}), fill = TRUE)
R_results_all_estimateR[, approach := "estimateR"]
```

```{r}
R_results_all <- rbindlist(list(R_results_all_EpiSewer, R_results_all_estimateR), fill = TRUE)

# add gold standard (full days)
R_results_all <- merge(R_results_all, R_results_all[subsampling_type == "5 days per week",c("wwtp", "target", "approach", "date", "median", "lower_0.95", "upper_0.95")], by = c("wwtp","target","approach","date"), suffixes = c("", "_full"), all.x = TRUE)

# add naive baseline (Rt=1)
scaled_baseline <- R_results_all[subsampling_type == "5 days per week" & approach == "EpiSewer",]
scaled_baseline[, baseline_error := median - 1]
R_results_all <- merge(R_results_all, scaled_baseline[, c("wwtp", "target", "date", "baseline_error")],
, by = c("wwtp","target","date"), all.x = TRUE)
```

```{r}
targets_select <- c("SARS-N2", "IAV-M", "RSV-N")
wave_dates <- readr::read_csv(here::here("data", "assumptions", "wave_dates.csv")) |> filter(season == "2023/24")
R_results_all <- merge(R_results_all, wave_dates, by = c("wwtp","target"))
R_results_all[, target := factor(target, levels = names(target_labels), labels = target_labels, ordered = TRUE)]
```
Quantitative results
```{r}
R_results_all[subsampling_type!="5 days per week" & date >= "2023-12-15" & date <= end_date, list(baseline_mean = mean(abs(median_full-1))), by = c("wwtp", "target", "approach")]

R_results_all[subsampling_type!="5 days per week" & date >= "2023-12-15" & date <= end_date, list(MAE = mean(abs(median-median_full))), by = c("wwtp", "target", "approach")]
```
MASE plot
```{r}
error_plot <- R_results_all[subsampling_type!="5 days per week" & date >= start_date & date <= end_date, list(MAE = mean(abs(median-median_full))/mean(abs(median_full-1))), by = c("wwtp", "target", "approach", "subsampling_type", "subsampling_subtype")] |> 
  ggplot(aes(x=approach, y = MAE, color = target)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_boxplot(outliers = FALSE) +
  geom_point(position = position_jitterdodge(jitter.height = 0, jitter.width = 0.2), size = 0.7) +
  ylab(expression(MASE~of~median~R[t])) +
  theme_bw() +
  facet_wrap(~ forcats::fct_rev(subsampling_type), nrow = 1) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    strip.background = element_rect(fill = "white")
    ) +
  scale_color_manual(values = palette_targets)
error_plot
```
Coverage plot
```{r}
coverage_plot <- R_results_all[subsampling_type!="5 days per week" & date>=start_date & date<=end_date, .(coverage = mean(upper_0.95>=median_full & lower_0.95<=median_full)), by = c("wwtp", "target", "approach", "subsampling_type", "subsampling_subtype")] |> 
ggplot(aes(x=approach, y = coverage, color = target)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_boxplot(outliers = FALSE) +
  geom_point(position = position_jitterdodge(jitter.height = 0, jitter.width = 0.2), size = 0.7) +
  ylab(expression(Mean~'95%'~CrI~coverage)) +
  theme_bw() +
  facet_wrap(~ forcats::fct_rev(subsampling_type), nrow = 1) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    strip.background = element_rect(fill = "white")
    ) +
  scale_color_manual(values = palette_targets, labels = c("SARS-CoV-2", "Influenza A virus", "Respiratory syncytial virus"))
coverage_plot
```

Width of uncertainty intervals
```{r}
width_plot <- R_results_all[subsampling_type!="5 days per week" & date>=start_date & date<=end_date, .(spread = mean(upper_0.95 - lower_0.95)), by = c("wwtp", "target", "approach", "subsampling_type", "subsampling_subtype")] |> 
  ggplot(aes(x=approach, y = spread, color = target)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(position = position_jitterdodge(jitter.height = 0)) +
  facet_wrap(~ forcats::fct_rev(subsampling_type), nrow = 1) +
  ylab("Mean width of 95% credible interval") +
  theme_bw() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.01, 0.99),
    legend.justification = c("left", "top"),
    legend.title = element_blank(),
    axis.title.x = element_blank()
    ) +
  scale_color_manual(values = palette_targets)
width_plot
```

## Example Rt estimates over time
```{r}
target_R_lim <- list(
  `SARS-N2` = c(0.7, 1.3),
  `IAV-M` = c(0.7, 1.5),
  `RSV-N` = c(0.6, 1.9)
)
```

```{r}
appraoch_select <- "EpiSewer"
subsampling_subtypes_selection <- c("(Monday|Tuesday)+(Wednesday|Thursday)+Friday" , "Friday", "Friday")
date_lim <- as.Date(c("2023-08-15", "2024-05-31"))

baseline <- R_results_all[approach == appraoch_select & subsampling_type == "5 days per week" & date>=date_lim[1] & date <= date_lim[2],]
baseline <- baseline[, subsampling_type := NULL]

example_subsampling_figure <- R_results_all |> distinct(approach, wwtp, target, date, subsampling_type, subsampling_subtype, .keep_all = TRUE) |> filter(approach == appraoch_select & subsampling_subtype %in% subsampling_subtypes_selection & date>=date_lim[1] & date <= date_lim[2]) |> 
  mutate(subsampling_type = factor(subsampling_type, levels = c("3 days per week", "1 day per week", "1 day per 2 weeks"))) |>
  ggplot(aes(x=date, y=median, color = target)) + 
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_ribbon(data = baseline, aes(ymin = lower_0.95, ymax = upper_0.95), fill = "black", alpha = 0.2, color = NA) +
  geom_ribbon(aes(ymin = lower_0.95, ymax = upper_0.95, fill = target), alpha = 0.2, color = NA) +
  geom_line(data = baseline, color = "black") +
  geom_line() +
  facet_grid(target ~ subsampling_type, scales = "free_y") +
  theme_bw() + 
  coord_cartesian(xlim = date_lim)  +
  scale_color_manual(values = palette_targets) +
  scale_fill_manual(values = palette_targets) +
  scale_x_date(date_breaks = "3 months", date_labels = "%m/%y", expand = c(0,0)) +
  ylab(expression(R[t])) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "white"),
    axis.title.x = element_blank()
    )
example_subsampling_figure
```

## Combined figure

```{r fig.width = 10, fig.height = 10}
metrics_plots <- cowplot::plot_grid(
  cowplot::plot_grid(plotlist = list(NULL, cowplot::get_plot_component(error_plot + theme(legend.position = "top"), pattern = "guide-box-top")), nrow = 1, rel_widths = c(0.1, 0.9)),
  cowplot::plot_grid(
    error_plot + theme(legend.position = "none"),
    coverage_plot + theme(legend.position = "none"),
    labels = c("B", "C"),
    nrow = 2, align = "v"), ncol = 1, rel_heights = c(0.05, 0.95), align = "v", axis = "lr")


cowplot::plot_grid(
    example_subsampling_figure, cowplot::plot_grid(metrics_plots, NULL, rel_widths = c(0.979, 0.021), nrow = 1),
  ncol = 1, labels = c("A", ""), rel_heights = c(0.5, 0.5), align = "v", axis = "tb"
)

ggsave(here::here("figures", "subsampling", "Fig_subsampling_combined.pdf"), width = 10, height = 10, scale = 0.9)
```

## Pruning
The following code can be used to clean the pipeline from unused objects

```{r}
for (pipeline in c("_subsampling")) {
  setup_pipeline(pipeline)
  tar_prune()
  prune_results(approach = "EpiSewer", remove_all_jobfiles = TRUE, remove_all_outputs = TRUE)
}
```
